Double-Drift Illusion Boundaries

### 2020-05-29 DoubleDriftResetLimits.Rmd
changed percept average plot to be split into time-constrained and space-constrained participants, added plot of reset-time distribution

>>>>

Here is a figure that splits participants by whether or not they have an average percept that is consistent with the data Lui et al found, and that is inconsistent with it.

```{r}
plotSplitDeviations()
```

Let's also have a look at the distribution of first reset points on Y-axis (~time). Sirui's model predicts a certain distribution of first reset points, so we can compare wat is measured here, with the model.

```{r}
plotResetYdistribution()
```
